---
title: "Introduction to Rseries"
author: "Diognes"
output:
  html_document:
    code_folding: hide
    toc: true # table of content true
    toc_depth: 3  # upto three depths of headings (specified by #, ## and ####)
    number_sections: true  ## if you want number sections at each table header
    # theme: united
    # highlight: tango  # specifies the syntax highlighting style
---

This vignette contains some examples about the use of Rseries package. 

# Brief explanation

```{r,echo=F,message=F,warning=F}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(RColorBrewer)
library(Rseries)

```



```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message=FALSE,fig.align="center", dpi=300)

```

We can select until 3 palette families at the moment: `palette_netflyx`, `palette_anime`,`palette_peru`. Each family is a list of palette from series. Each palette in this package have a total of 6 colors. In brief the total list of palettes avaliable per family is :

```{r,echo=F,warning=F,message=F}
show_pal(palette_family = palette_netflyx)
```

```{r,echo=F,warning=F,message=F}
show_pal(palette_family = palette_anime)
```

```{r,echo=F,warning=F,message=F}
show_pal(palette_family = palette_peru)
```



With the function `serie_palette` we can select a palette from a specific family following this entry:

`serie_palette( enter name, palette of preference, palette family ,number of colors, type discrete or continous )`

Let's see some examples using ggplot2 based on [the R Graph Gallery
](https://r-graph-gallery.com/) examples.


---

# Libraries

```{r,warning=F,message=F, class.source = 'fold-show'}

# Libraries
library(tidyverse)
library(ggplot2)
library(dplyr)
library(RColorBrewer)
library(Rseries)

```

---

# Netflyx palette family

## Palette: `Lupin` {.tabset}

### Some time series

```{r}
EuStockMarkets %>%
  as.data.frame() %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4)) %>% 
  ggplot() +
  geom_line(aes(color = index,x=time,y=price), size = 1) +
  scale_color_rseries(palette = "Lupin", palette_family = palette_netflyx) +
  theme_minimal()
```

### A classic boxplot

```{r}
# create a dataset
data <- data.frame(
  name=c( rep("A",500), rep("B",500), rep("B",500), rep("C",20), rep('D', 100)),
  value=c( rnorm(500, 10, 5), rnorm(500, 13, 1), rnorm(500, 18, 1), rnorm(20, 25, 4), rnorm(100, 12, 1) )
)

# Plot
data %>%
  ggplot( aes(x=name, y=value, fill=name)) +
    geom_boxplot() +
    scale_fill_rseries(palette_family = palette_netflyx, palette = "Lupin") +
    theme_classic() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    ggtitle("A classic boxplot") +
    xlab(" ")
```


### Some density charts

```{r}
# Libraries
library(tidyverse)
library(ggplot2)
library(Rseries)

# Using the diamods dataset we can some of the palettes in our package.

# Multi density chart
p1 <- ggplot(diamonds, aes(x=price,fill=cut))+
  geom_density(position='stack')+
      scale_fill_rseries(palette_family = palette_netflyx, palette = "Lupin") +
  theme_minimal()
p1

# Stacked density plot
p2 <- ggplot(data=diamonds, aes(x=price, group=cut, fill=cut)) +
    geom_density(adjust=1.5, position="fill") +
        scale_fill_rseries(palette_family = palette_netflyx, palette = "Lupin") +
    theme_minimal()
p2
```

### Some data art

```{r}
# Libraries
library(ggplot2)
library(RColorBrewer)

# create a dataset
set.seed(345)
ngroup=30
names=paste("G_",seq(1,ngroup),sep="")
DAT=data.frame()

for(i in seq(1:30)){
  data=data.frame( matrix(0, ngroup , 3))
  data[,1]=i
  data[,2]=sample(names, nrow(data))
  data[,3]=prop.table(sample( c(rep(0,113),c(1:ngroup)) ,nrow(data)))
  DAT=rbind(DAT,data)
}
colnames(DAT)=c("Year","Group","Value")
DAT=DAT[order( DAT$Year, DAT$Group) , ]

# plot
pal = serie_palette("Lupin", palette_netflyx, 12)
pal = colorRampPalette(pal)(ngroup)
pal=pal[sample(c(1:length(pal)) , size=length(pal) ) ]

ggplot(DAT, aes(x=Year, y=Value, fill=Group )) + 
  geom_area(alpha=1)+
  theme_bw() +
  scale_fill_manual(values = pal)+
  theme(
    text = element_blank(),
    line = element_blank(),
    title = element_blank(),
    legend.position="none",
    panel.border = element_blank(),
    panel.background = element_blank())
```


## Palette: `GambitoDama` {.tabset}

### Some time series

```{r}
EuStockMarkets %>%
  as.data.frame() %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4)) %>% 
  ggplot() +
  geom_line(aes(color = index,x=time,y=price), size = 1) +
  scale_color_rseries(palette = "GambitoDama", palette_family = palette_netflyx) +
  theme_minimal()
```

### A classic boxplot

```{r}
# create a dataset
data <- data.frame(
  name=c( rep("A",500), rep("B",500), rep("B",500), rep("C",20), rep('D', 100)),
  value=c( rnorm(500, 10, 5), rnorm(500, 13, 1), rnorm(500, 18, 1), rnorm(20, 25, 4), rnorm(100, 12, 1) )
)

# Plot
data %>%
  ggplot( aes(x=name, y=value, fill=name)) +
    geom_boxplot() +
    scale_fill_rseries(palette_family = palette_netflyx, palette = "GambitoDama") +
    theme_classic() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    ggtitle("A classic boxplot") +
    xlab(" ")
```


### Some density charts

```{r}
# Libraries
library(tidyverse)
library(ggplot2)
library(Rseries)

# Using the diamods dataset we can some of the palettes in our package.

# Multi density chart
p1 <- ggplot(diamonds, aes(x=price,fill=cut))+
  geom_density(position='stack')+
      scale_fill_rseries(palette_family = palette_netflyx, palette = "GambitoDama") +
  theme_minimal()
p1

# Stacked density plot
p2 <- ggplot(data=diamonds, aes(x=price, group=cut, fill=cut)) +
    geom_density(adjust=1.5, position="fill") +
        scale_fill_rseries(palette_family = palette_netflyx, palette = "GambitoDama") +
    theme_minimal()
p2
```

### Some data art

```{r}
# Libraries
library(ggplot2)
library(RColorBrewer)

# create a dataset
set.seed(345)
ngroup=30
names=paste("G_",seq(1,ngroup),sep="")
DAT=data.frame()

for(i in seq(1:30)){
  data=data.frame( matrix(0, ngroup , 3))
  data[,1]=i
  data[,2]=sample(names, nrow(data))
  data[,3]=prop.table(sample( c(rep(0,113),c(1:ngroup)) ,nrow(data)))
  DAT=rbind(DAT,data)
}
colnames(DAT)=c("Year","Group","Value")
DAT=DAT[order( DAT$Year, DAT$Group) , ]

# plot
pal = serie_palette("GambitoDama", palette_netflyx, 12)
pal = colorRampPalette(pal)(ngroup)
pal=pal[sample(c(1:length(pal)) , size=length(pal) ) ]

ggplot(DAT, aes(x=Year, y=Value, fill=Group )) + 
  geom_area(alpha=1)+
  theme_bw() +
  scale_fill_manual(values = pal)+
  theme(
    text = element_blank(),
    line = element_blank(),
    title = element_blank(),
    legend.position="none",
    panel.border = element_blank(),
    panel.background = element_blank())
```


## Palette: `Ozark` {.tabset}

### Some time series

```{r}
EuStockMarkets %>%
  as.data.frame() %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4)) %>% 
  ggplot() +
  geom_line(aes(color = index,x=time,y=price), size = 1) +
  scale_color_rseries(palette = "Ozark", palette_family = palette_netflyx) +
  theme_minimal()
```

### A classic boxplot

```{r}
# create a dataset
data <- data.frame(
  name=c( rep("A",500), rep("B",500), rep("B",500), rep("C",20), rep('D', 100)),
  value=c( rnorm(500, 10, 5), rnorm(500, 13, 1), rnorm(500, 18, 1), rnorm(20, 25, 4), rnorm(100, 12, 1) )
)

# Plot
data %>%
  ggplot( aes(x=name, y=value, fill=name)) +
    geom_boxplot() +
    scale_fill_rseries(palette_family = palette_netflyx, palette = "Ozark") +
    theme_classic() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    ggtitle("A classic boxplot") +
    xlab(" ")
```


### Some density charts

```{r}
# Libraries
library(tidyverse)
library(ggplot2)
library(Rseries)

# Using the diamods dataset we can some of the palettes in our package.

# Multi density chart
p1 <- ggplot(diamonds, aes(x=price,fill=cut))+
  geom_density(position='stack')+
      scale_fill_rseries(palette_family = palette_netflyx, palette = "Ozark") +
  theme_minimal()
p1

# Stacked density plot
p2 <- ggplot(data=diamonds, aes(x=price, group=cut, fill=cut)) +
    geom_density(adjust=1.5, position="fill") +
        scale_fill_rseries(palette_family = palette_netflyx, palette = "Ozark") +
    theme_minimal()
p2
```

### Some data art

```{r}
# Libraries
library(ggplot2)
library(RColorBrewer)

# create a dataset
set.seed(345)
ngroup=30
names=paste("G_",seq(1,ngroup),sep="")
DAT=data.frame()

for(i in seq(1:30)){
  data=data.frame( matrix(0, ngroup , 3))
  data[,1]=i
  data[,2]=sample(names, nrow(data))
  data[,3]=prop.table(sample( c(rep(0,113),c(1:ngroup)) ,nrow(data)))
  DAT=rbind(DAT,data)
}
colnames(DAT)=c("Year","Group","Value")
DAT=DAT[order( DAT$Year, DAT$Group) , ]

# plot
pal = serie_palette("Ozark", palette_netflyx, 12)
pal = colorRampPalette(pal)(ngroup)
pal=pal[sample(c(1:length(pal)) , size=length(pal) ) ]

ggplot(DAT, aes(x=Year, y=Value, fill=Group )) + 
  geom_area(alpha=1)+
  theme_bw() +
  scale_fill_manual(values = pal)+
  theme(
    text = element_blank(),
    line = element_blank(),
    title = element_blank(),
    legend.position="none",
    panel.border = element_blank(),
    panel.background = element_blank())
```





---

# Anime palette family


## Palette: `poputepik` {.tabset}

### Some time series

```{r}
EuStockMarkets %>%
  as.data.frame() %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4)) %>% 
  ggplot() +
  geom_line(aes(color = index,x=time,y=price), size = 1) +
  scale_color_rseries(palette = "poputepik", palette_family = palette_anime) +
  theme_minimal()
```

### A classic boxplot

```{r}
# Libraries
library(tidyverse)
library(ggplot2)
library(Rseries)

# create a dataset
data <- data.frame(
  name=c( rep("A",500), rep("B",500), rep("B",500), rep("C",20), rep('D', 100)),
  value=c( rnorm(500, 10, 5), rnorm(500, 13, 1), rnorm(500, 18, 1), rnorm(20, 25, 4), rnorm(100, 12, 1) )
)

# Plot
pal=serie_palette("poputepik", palette_anime, 5)

data %>%
  ggplot( aes(x=name, y=value, fill=name)) +
    geom_boxplot() +
    scale_fill_manual(values=(pal)) +
    theme_classic() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    ggtitle("A classic boxplot") +
    xlab("")
```


### Some density charts

```{r}
# Libraries
library(tidyverse)
library(ggplot2)
library(Rseries)

pal=serie_palette("poputepik", palette_anime, 5)

# Using the diamods dataset we can some of the palettes in our package.

# Multi density chart
p1 <- ggplot(diamonds, aes(x=price,fill=cut))+
  geom_density(position='stack')+
  scale_fill_manual(values=(pal))+
  theme_minimal()
p1

# Stacked density plot
p2 <- ggplot(data=diamonds, aes(x=price, group=cut, fill=cut)) +
    geom_density(adjust=1.5, position="fill") +
    scale_fill_manual(values=(pal)) +
    theme_minimal()
p2
```

### Some data art

```{r}
# Libraries
library(ggplot2)
library(RColorBrewer)

# create a dataset
set.seed(345)
ngroup=30
names=paste("G_",seq(1,ngroup),sep="")
DAT=data.frame()

for(i in seq(1:30)){
  data=data.frame( matrix(0, ngroup , 3))
  data[,1]=i
  data[,2]=sample(names, nrow(data))
  data[,3]=prop.table(sample( c(rep(0,113),c(1:ngroup)) ,nrow(data)))
  DAT=rbind(DAT,data)
}
colnames(DAT)=c("Year","Group","Value")
DAT=DAT[order( DAT$Year, DAT$Group) , ]

# plot
pal = serie_palette("poputepik", palette_anime, 6)
pal = colorRampPalette(pal)(ngroup)
pal=pal[sample(c(1:length(pal)) , size=length(pal) ) ]

ggplot(DAT, aes(x=Year, y=Value, fill=Group )) + 
  geom_area(alpha=1)+
  theme_bw() +
  scale_fill_manual(values = pal)+
  theme(
    text = element_blank(),
    line = element_blank(),
    title = element_blank(),
    legend.position="none",
    panel.border = element_blank(),
    panel.background = element_blank())
```




## Palette: `tokyorev` {.tabset}

### Some time series

```{r}
EuStockMarkets %>%
  as.data.frame() %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4)) %>% 
  ggplot() +
  geom_line(aes(color = index,x=time,y=price), size = 1) +
  scale_color_rseries(palette = "tokyorev", palette_family = palette_anime) +
  theme_minimal()
```

### A classic boxplot

```{r}
# Libraries
library(tidyverse)
library(ggplot2)
library(Rseries)

# create a dataset
data <- data.frame(
  name=c( rep("Shibuya",500), rep("Shinjuku",500), rep("Yokohama",500), rep("Umishita Park",20), rep('Musashi Shrine', 100)),
  value=c( rnorm(500, 10, 5), rnorm(500, 13, 1), rnorm(500, 18, 1), rnorm(20, 25, 4), rnorm(100, 12, 1) )
)

# Plot
pal=serie_palette("tokyorev", palette_anime, 5)

data %>%
  ggplot( aes(x=name, y=value, fill=name)) +
    geom_boxplot() +
    scale_fill_manual(values=(pal)) +
    theme_classic() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    ggtitle("A classic boxplot") +
    xlab("")
```


### Some density charts

```{r}
# Libraries
library(tidyverse)
library(ggplot2)
library(Rseries)

pal=serie_palette("tokyorev", palette_anime, 5)

# Using the diamods dataset we can some of the palettes in our package.

# Multi density chart
p1 <- ggplot(diamonds, aes(x=price,fill=cut))+
  geom_density(position='stack')+
  scale_fill_manual(values=(pal))+
  theme_minimal()
p1

# Stacked density plot
p2 <- ggplot(data=diamonds, aes(x=price, group=cut, fill=cut)) +
    geom_density(adjust=1.5, position="fill") +
    scale_fill_manual(values=(pal)) +
    theme_minimal()
p2
```

### Some data art

```{r}
# Libraries
library(ggplot2)
library(RColorBrewer)

# create a dataset
set.seed(345)
ngroup=30
names=paste("G_",seq(1,ngroup),sep="")
DAT=data.frame()

for(i in seq(1:30)){
  data=data.frame( matrix(0, ngroup , 3))
  data[,1]=i
  data[,2]=sample(names, nrow(data))
  data[,3]=prop.table(sample( c(rep(0,113),c(1:ngroup)) ,nrow(data)))
  DAT=rbind(DAT,data)
}
colnames(DAT)=c("Year","Group","Value")
DAT=DAT[order( DAT$Year, DAT$Group) , ]

# plot
pal = serie_palette("tokyorev", palette_anime, 6)
pal = colorRampPalette(pal)(ngroup)
pal=pal[sample(c(1:length(pal)) , size=length(pal) ) ]

ggplot(DAT, aes(x=Year, y=Value, fill=Group )) + 
  geom_area(alpha=1)+
  theme_bw() +
  scale_fill_manual(values = pal)+
  theme(
    text = element_blank(),
    line = element_blank(),
    title = element_blank(),
    legend.position="none",
    panel.border = element_blank(),
    panel.background = element_blank())
```




## Palette: `yona` {.tabset}

### Some time series

```{r}
EuStockMarkets %>%
  as.data.frame() %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4)) %>% 
  ggplot() +
  geom_line(aes(color = index,x=time,y=price), size = 1) +
  scale_color_rseries(palette = "yona", palette_family = palette_anime) +
  theme_minimal()
```

### A classic boxplot

```{r}
# Libraries
library(tidyverse)
library(ggplot2)
library(Rseries)

# create a dataset
data <- data.frame(
  name=c( rep("Kouka Kingdom",500), rep("Wind Tribe",500), rep("Water Tribe",500), rep("Fire Tribe",20), rep('Kai Empire', 100)),
  value=c( rnorm(500, 10, 5), rnorm(500, 13, 1), rnorm(500, 18, 1), rnorm(20, 25, 4), rnorm(100, 12, 1) )
)

# Plot
pal=serie_palette("yona", palette_anime, 5)

data %>%
  ggplot( aes(x=name, y=value, fill=name)) +
    geom_boxplot() +
    scale_fill_manual(values=(pal)) +
    theme_classic() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    ggtitle("A classic boxplot") +
    xlab("")
```


### Some density charts

```{r}
# Libraries
library(tidyverse)
library(ggplot2)
library(Rseries)

pal=serie_palette("yona", palette_anime, 5)

# Using the diamods dataset we can some of the palettes in our package.

# Multi density chart
p1 <- ggplot(diamonds, aes(x=price,fill=cut))+
  geom_density(position='stack')+
  scale_fill_manual(values=(pal))+
  theme_minimal()
p1

# Stacked density plot
p2 <- ggplot(data=diamonds, aes(x=price, group=cut, fill=cut)) +
    geom_density(adjust=1.5, position="fill") +
    scale_fill_manual(values=(pal)) +
    theme_minimal()
p2
```

### Some data art

```{r}
# Libraries
library(ggplot2)
library(RColorBrewer)

# create a dataset
set.seed(345)
ngroup=30
names=paste("G_",seq(1,ngroup),sep="")
DAT=data.frame()

for(i in seq(1:30)){
  data=data.frame( matrix(0, ngroup , 3))
  data[,1]=i
  data[,2]=sample(names, nrow(data))
  data[,3]=prop.table(sample( c(rep(0,113),c(1:ngroup)) ,nrow(data)))
  DAT=rbind(DAT,data)
}
colnames(DAT)=c("Year","Group","Value")
DAT=DAT[order( DAT$Year, DAT$Group) , ]

# plot
pal = serie_palette("yona", palette_anime, 6)
pal = colorRampPalette(pal)(ngroup)
pal=pal[sample(c(1:length(pal)) , size=length(pal) ) ]

ggplot(DAT, aes(x=Year, y=Value, fill=Group )) + 
  geom_area(alpha=1)+
  theme_bw() +
  scale_fill_manual(values = pal)+
  theme(
    text = element_blank(),
    line = element_blank(),
    title = element_blank(),
    legend.position="none",
    panel.border = element_blank(),
    panel.background = element_blank())
```





# Peru palette family


## Palette: `AlFondoHaySitio` {.tabset}

### Some time series

```{r}
EuStockMarkets %>%
  as.data.frame() %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4)) %>% 
  ggplot() +
  geom_line(aes(color = index,x=time,y=price), size = 1) +
  scale_color_rseries(palette = "AlFondoHaySitio", palette_family = palette_peru) +
  theme_minimal()
```

### A classic boxplot

```{r}
# Libraries
library(tidyverse)
library(ggplot2)
library(Rseries)

# create a dataset
data <- data.frame(
  name=c( rep("A",500), rep("B",500), rep("B",500), rep("C",20), rep('D', 100)),
  value=c( rnorm(500, 10, 5), rnorm(500, 13, 1), rnorm(500, 18, 1), rnorm(20, 25, 4), rnorm(100, 12, 1) )
)

# Plot
pal=serie_palette("AlFondoHaySitio", palette_peru, 5)

data %>%
  ggplot( aes(x=name, y=value, fill=name)) +
    geom_boxplot() +
    scale_fill_manual(values=(pal)) +
    theme_classic() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    ggtitle("A classic boxplot") +
    xlab("")
```


### Some density charts

```{r}
# Libraries
library(tidyverse)
library(ggplot2)
library(Rseries)

pal=serie_palette("AlFondoHaySitio", palette_peru, 5)

# Using the diamods dataset we can some of the palettes in our package.

# Multi density chart
p1 <- ggplot(diamonds, aes(x=price,fill=cut))+
  geom_density(position='stack')+
  scale_fill_manual(values=(pal))+
  theme_minimal()
p1

# Stacked density plot
p2 <- ggplot(data=diamonds, aes(x=price, group=cut, fill=cut)) +
    geom_density(adjust=1.5, position="fill") +
    scale_fill_manual(values=(pal)) +
    theme_minimal()
p2
```

### Some data art

```{r}
# Libraries
library(ggplot2)
library(RColorBrewer)

# create a dataset
set.seed(345)
ngroup=30
names=paste("G_",seq(1,ngroup),sep="")
DAT=data.frame()

for(i in seq(1:30)){
  data=data.frame( matrix(0, ngroup , 3))
  data[,1]=i
  data[,2]=sample(names, nrow(data))
  data[,3]=prop.table(sample( c(rep(0,113),c(1:ngroup)) ,nrow(data)))
  DAT=rbind(DAT,data)
}
colnames(DAT)=c("Year","Group","Value")
DAT=DAT[order( DAT$Year, DAT$Group) , ]

# plot
pal = serie_palette("AlFondoHaySitio", palette_peru, 6)
pal = colorRampPalette(pal)(ngroup)
pal=pal[sample(c(1:length(pal)) , size=length(pal) ) ]

ggplot(DAT, aes(x=Year, y=Value, fill=Group )) + 
  geom_area(alpha=1)+
  theme_bw() +
  scale_fill_manual(values = pal)+
  theme(
    text = element_blank(),
    line = element_blank(),
    title = element_blank(),
    legend.position="none",
    panel.border = element_blank(),
    panel.background = element_blank())
```





## Palette: `DeVueltaBarrio` {.tabset}

### Some time series

```{r}
EuStockMarkets %>%
  as.data.frame() %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4)) %>% 
  ggplot() +
  geom_line(aes(color = index,x=time,y=price), size = 1) +
  scale_color_rseries(palette = "DeVueltaBarrio", palette_family = palette_peru) +
  theme_minimal()
```

### A classic boxplot

```{r}
# Libraries
library(tidyverse)
library(ggplot2)
library(Rseries)

# create a dataset
data <- data.frame(
  name=c( rep("Shibuya",500), rep("Shinjuku",500), rep("Yokohama",500), rep("Umishita Park",20), rep('Musashi Shrine', 100)),
  value=c( rnorm(500, 10, 5), rnorm(500, 13, 1), rnorm(500, 18, 1), rnorm(20, 25, 4), rnorm(100, 12, 1) )
)

# Plot
pal=serie_palette("DeVueltaBarrio", palette_peru, 5)

data %>%
  ggplot( aes(x=name, y=value, fill=name)) +
    geom_boxplot() +
    scale_fill_manual(values=(pal)) +
    theme_classic() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    ggtitle("A classic boxplot") +
    xlab("")
```


### Some density charts

```{r}
# Libraries
library(tidyverse)
library(ggplot2)
library(Rseries)

pal=serie_palette("DeVueltaBarrio", palette_peru, 5)

# Using the diamods dataset we can some of the palettes in our package.

# Multi density chart
p1 <- ggplot(diamonds, aes(x=price,fill=cut))+
  geom_density(position='stack')+
  scale_fill_manual(values=(pal))+
  theme_minimal()
p1

# Stacked density plot
p2 <- ggplot(data=diamonds, aes(x=price, group=cut, fill=cut)) +
    geom_density(adjust=1.5, position="fill") +
    scale_fill_manual(values=(pal)) +
    theme_minimal()
p2
```

### Some data art

```{r}
# Libraries
library(ggplot2)
library(RColorBrewer)

# create a dataset
set.seed(345)
ngroup=30
names=paste("G_",seq(1,ngroup),sep="")
DAT=data.frame()

for(i in seq(1:30)){
  data=data.frame( matrix(0, ngroup , 3))
  data[,1]=i
  data[,2]=sample(names, nrow(data))
  data[,3]=prop.table(sample( c(rep(0,113),c(1:ngroup)) ,nrow(data)))
  DAT=rbind(DAT,data)
}
colnames(DAT)=c("Year","Group","Value")
DAT=DAT[order( DAT$Year, DAT$Group) , ]

# plot
pal = serie_palette("DeVueltaBarrio", palette_peru, 6)
pal = colorRampPalette(pal)(ngroup)
pal=pal[sample(c(1:length(pal)) , size=length(pal) ) ]

ggplot(DAT, aes(x=Year, y=Value, fill=Group )) + 
  geom_area(alpha=1)+
  theme_bw() +
  scale_fill_manual(values = pal)+
  theme(
    text = element_blank(),
    line = element_blank(),
    title = element_blank(),
    legend.position="none",
    panel.border = element_blank(),
    panel.background = element_blank())
```




## Palette: `MilOficios` {.tabset}

### Some time series

```{r}
EuStockMarkets %>%
  as.data.frame() %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4)) %>% 
  ggplot() +
  geom_line(aes(color = index,x=time,y=price), size = 1) +
  scale_color_rseries(palette = "MilOficios", palette_family = palette_peru) +
  theme_minimal()
```

### A classic boxplot

```{r}
# Libraries
library(tidyverse)
library(ggplot2)
library(Rseries)

# create a dataset
data <- data.frame(
  name=c( rep("Kouka Kingdom",500), rep("Wind Tribe",500), rep("Water Tribe",500), rep("Fire Tribe",20), rep('Kai Empire', 100)),
  value=c( rnorm(500, 10, 5), rnorm(500, 13, 1), rnorm(500, 18, 1), rnorm(20, 25, 4), rnorm(100, 12, 1) )
)

# Plot
pal=serie_palette("MilOficios", palette_peru, 5)

data %>%
  ggplot( aes(x=name, y=value, fill=name)) +
    geom_boxplot() +
    scale_fill_manual(values=(pal)) +
    theme_classic() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    ggtitle("A classic boxplot") +
    xlab("")
```


### Some density charts

```{r}
# Libraries
library(tidyverse)
library(ggplot2)
library(Rseries)

pal=serie_palette("MilOficios", palette_peru, 5)

# Using the diamods dataset we can some of the palettes in our package.

# Multi density chart
p1 <- ggplot(diamonds, aes(x=price,fill=cut))+
  geom_density(position='stack')+
  scale_fill_manual(values=(pal))+
  theme_minimal()
p1

# Stacked density plot
p2 <- ggplot(data=diamonds, aes(x=price, group=cut, fill=cut)) +
    geom_density(adjust=1.5, position="fill") +
    scale_fill_manual(values=(pal)) +
    theme_minimal()
p2
```

### Some data art

```{r}
# Libraries
library(ggplot2)
library(RColorBrewer)

# create a dataset
set.seed(345)
ngroup=30
names=paste("G_",seq(1,ngroup),sep="")
DAT=data.frame()

for(i in seq(1:30)){
  data=data.frame( matrix(0, ngroup , 3))
  data[,1]=i
  data[,2]=sample(names, nrow(data))
  data[,3]=prop.table(sample( c(rep(0,113),c(1:ngroup)) ,nrow(data)))
  DAT=rbind(DAT,data)
}
colnames(DAT)=c("Year","Group","Value")
DAT=DAT[order( DAT$Year, DAT$Group) , ]

# plot
pal = serie_palette("MilOficios", palette_peru, 6)
pal = colorRampPalette(pal)(ngroup)
pal=pal[sample(c(1:length(pal)) , size=length(pal) ) ]

ggplot(DAT, aes(x=Year, y=Value, fill=Group )) + 
  geom_area(alpha=1)+
  theme_bw() +
  scale_fill_manual(values = pal)+
  theme(
    text = element_blank(),
    line = element_blank(),
    title = element_blank(),
    legend.position="none",
    panel.border = element_blank(),
    panel.background = element_blank())
```




---



# Functions for fill and color aesthetics

```{r}
diamonds %>% 
  ggplot(aes(x = cut, fill = clarity)) +
  geom_bar() +
  scale_fill_rseries()+
  theme_bw() +
  ggtitle('scale_fill_rseries()')
```



```{r}
EuStockMarkets %>%
  as.data.frame() %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4)) %>% 
  ggplot()+
  geom_line(aes(color = index,x=time,y=price), size = 1) +
  scale_color_rseries(palette = "tokyorev",
                      palette_family = palette_anime)  +
  theme_minimal()
```


